### 2023-02-18 main.tex
observation
Q0 Q\Delta

We rewrite
\begin{equation}
	\begin{split}
	D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}+2(N-1)e_{ii}^{tot}
\end{split}
\end{equation}
then
\begin{equation}
\begin{split}
\boxed{D_{ii}^{2L-1}=	2Ne_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}}
	\end{split}
\end{equation}
%The following \textit{lower diagonal} elements of $U_{0}(x)$, $\forall i=2,\ldots,L$ and for $j=1$
%\begin{equation}
%	C_{i}(x)=C_{i}^{2L-1}x^{2L-1}+\ldots
%\end{equation}
%where the coefficient is
%\begin{equation}\label{c}
%	C_{i}^{2L-1}=2e_{1i}^{tot}+2\sum_{a< b}\left(e_{1i}^{[a]}e_{11}^{[b]}-e_{1i}^{[a]}e_{ii}^{[b]}-\sum_{k=2\,:\,k\neq j}^{N}e_{1k}^{[a]}e_{ki}^{[b]}\right)
%\end{equation}
Moreover, $\forall j=2,\ldots,L$ and for $i=1$
\begin{equation}
	B_{j}(x)=B_{j}^{2L-1}x^{2L-1}+\ldots
\end{equation}
where the coefficient is 
\begin{equation}\label{b}
\begin{split}
	B_{j}^{2L-1}&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-e_{j1}^{[a]}e_{jj}^{[b]}-\sum_{k=2\,:\,k\neq j}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)\\
	&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-\sum_{k=2}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)
\end{split}
\end{equation}
then
\begin{equation}
\begin{split}
	\boxed{B_{j}^{2L-1}=2e_{j1}^{tot}+
	2\sum_{a,b=1\,:\, a<b}^{L}e_{j1}^{[a]}e_{11}^{[b]}-2\sum_{a,b=1\,:\, a>b}^{L}\sum_{k=2}^{N}e_{jk}^{[a]}e_{k1}^{[b]}}
\end{split}
\end{equation}
\textbf{Remark}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\
The interesting charges (we only look for the first non trivial one) take the following form

\begin{align}
	Q_{2L+2}&=A^{2L+1}-\sum_{i=2}^{N}D_{ii}^{2L+1}\\
	Q_{2L+1}&=NA^{2L+1}+A^{2L}-\sum_{i=2}^{N}D_{ii}^{2L}\\
	Q_{2L}&=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}+\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{align}
The charges $Q_{2L+2}$ and $Q_{2L+1}$ are proportional to the identity matrix, while $Q_{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=2,\ldots,N$.\\
It is easy to show that 
\begin{equation}
	\left[Q_{2L},\widetilde{H}\right]=Q_{2L}\widetilde{H}-\widetilde{H}Q_{2L}=0
\end{equation}
The commutation with the Hamiltonian $\widetilde{H}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. 
\section{Conclusion}

>>>>

We rewrite
\begin{equation}
	\begin{split}
	D_{ii}^{2L-1}&=2e_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}+2(N-1)e_{ii}^{tot}
\end{split}
\end{equation}
then
\begin{equation}
\begin{split}
\boxed{D_{ii}^{2L-1}=	2Ne_{ii}^{tot}+\left(e_{11}^{tot}-\sum_{j=2}^{N}e_{jj}^{tot}\right)-2\sum_{j=2}^{N}e_{ij}^{tot}e_{ji}^{tot}}
	\end{split}
\end{equation}
\textbf{Observation}: it seems to me that, although not diagonal, the $D_{ii}^{2L-1}$ does not chaing the exitation of the chain since we have $e_{ij}^{tot}e_{ji}^{tot}$!\\
%The following \textit{lower diagonal} elements of $U_{0}(x)$, $\forall i=2,\ldots,L$ and for $j=1$
%\begin{equation}
%	C_{i}(x)=C_{i}^{2L-1}x^{2L-1}+\ldots
%\end{equation}
%where the coefficient is
%\begin{equation}\label{c}
%	C_{i}^{2L-1}=2e_{1i}^{tot}+2\sum_{a< b}\left(e_{1i}^{[a]}e_{11}^{[b]}-e_{1i}^{[a]}e_{ii}^{[b]}-\sum_{k=2\,:\,k\neq j}^{N}e_{1k}^{[a]}e_{ki}^{[b]}\right)
%\end{equation}
Moreover, $\forall j=2,\ldots,L$ and for $i=1$
\begin{equation}
	B_{j}(x)=B_{j}^{2L-1}x^{2L-1}+\ldots
\end{equation}
where the coefficient is 
\begin{equation}\label{b}
\begin{split}
	B_{j}^{2L-1}&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-e_{j1}^{[a]}e_{jj}^{[b]}-\sum_{k=2\,:\,k\neq j}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)\\
	&=2e_{j1}^{tot}+2\sum_{a< b}\left(e_{j1}^{[a]}e_{11}^{[b]}-\sum_{k=2}^{N}e_{k1}^{[a]}e_{jk}^{[b]}\right)
\end{split}
\end{equation}
then
\begin{equation}
\begin{split}
	\boxed{B_{j}^{2L-1}=2e_{j1}^{tot}+
	2\sum_{a,b=1\,:\, a<b}^{L}e_{j1}^{[a]}e_{11}^{[b]}-2\sum_{a,b=1\,:\, a>b}^{L}\sum_{k=2}^{N}e_{jk}^{[a]}e_{k1}^{[b]}}
\end{split}
\end{equation}
\textbf{Remark}: it is easy to see that, when restricted to the case of 2 species,  \eqref{a2lp},\eqref{a2l},\eqref{a2lm1} correspond to the one compute in \cite{frassek2020eigenstates}. \\ \\
The interesting charges (we only look for the first non trivial one) take the following form

\begin{align}
	Q_{2L+2}&=A^{2L+1}-\sum_{i=2}^{N}D_{ii}^{2L+1}\\
	Q_{2L+1}&=NA^{2L+1}+A^{2L}-\sum_{i=2}^{N}D_{ii}^{2L}\\
	Q_{2L}&=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}+\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{align}
The charges $Q_{2L+2}$ and $Q_{2L+1}$ are proportional to the identity matrix, while $Q_{2L}$ contains non diagonal matrices and the boundary parameters $\alpha_{i},\beta_{i}$ $\forall i=2,\ldots,N$.\\
It is easy to show that 
\begin{equation}
	\left[Q_{2L},\widetilde{H}\right]=Q_{2L}\widetilde{H}-\widetilde{H}Q_{2L}=0
\end{equation}
The commutation with the Hamiltonian $\widetilde{H}$ for $Q_{2L+2}$ and $Q_{2L+1}$ is trivial. \\
We introduce the following:
\begin{equation}
Q_{2}^{0}:=NA^{2L}+A^{2L-1}-\sum_{i=2}^{N}D_{ii}^{2L-1}
\end{equation}
it has the property that commute with the equilibrium Hamiltonian
\begin{equation}
\widetilde{H}_{0}:=\widetilde{B}_{1}^{0}+\mathcal{H}+\widetilde{B}_{L}
\end{equation}
where 
\begin{equation}
\widetilde{B}_{1}^{0}=\begin{pmatrix}
0&0&\ldots&0\\
0&-1&\ldots&0\\
\vdots&\vdots&\ddots&\vdots\\
0&0&\ldots&-1
\end{pmatrix}
\end{equation}
i.e.
\begin{equation}
\left[Q_{2}^{0},\widetilde{H}_{0}\right]=Q_{2}^{0}\widetilde{H}_{0}-\widetilde{H}_{0}Q_{2}^{0}=0
\end{equation}
We also introduce 
\begin{equation}
Q_{2}^{\Delta}:=\sum_{i=2}^{N}2(\alpha_{i}-\beta_{i})B_{i}^{2L-1}
\end{equation}
These two matrices $Q_{2}^{0}$ and $Q_{2}^{\Delta}$ are such that
\begin{equation}
Q_{2}=Q_{2}^{0}+Q_{2}^{\Delta}
\end{equation}
\section{Conclusion}
